---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ldscR

<!-- badges: start -->
[![R-CMD-check](https://github.com/mglev1n/ldscR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mglev1n/ldscR/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/mglev1n/ldscR/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/mglev1n/ldscR/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The goal of ldscR is to provide functionality to perform heritability estimation using LD score
regression within R.

## Installation

You can install the development version of ldscR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mglev1n/ldscR")
```

## Usage

`ldsc_h2()` can be used to estimate heritability. Sample GWAS data is provided in `sumstats_munged_example()`. Users can utilize built-in LD reference data, or provide their own.


```{r example, eval=FALSE}
library(ldscR)
df <- sumstats_munged_example()
ldsc_h2(munged_sumstats = df, ancestry = "EUR")
```

